Quality Definitions of Qualities

### 2021-10-01 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updates to installability rationale

\begin{abstract}
	Existing definitions of software qualities (also called quality
  characteristics) are collected and analyzed.  For each quality a
  ``best'\rq{} definition is recommended based on the following criteria:
  unambiguity, simplicity, consistency, ...
\end{abstract}

@@

Quality is defined as a measure of the excellence or worth of an entity.  As is
standard practice, we do not think of quality as a single measure, but rather as
a set of measures.  That is, quality is a collection of different qualities,
often called ``ilities.''  In the overview of managing software quality provided
by \citet[p 110]{VanVliet2000} the different measures are called quality
attributes, quality factors, and quality criteria.  In \citet{ISO9126} they are
called quality characteristics, sub-characteristics and attributes.  To keep our
presentation simple, and to not imply a classification hierarchy that we don't
intend, we will just use the term qualities to refer to the different measures
of quality.

The qualities of most interest to project managers and users are summarized in
the next subsection (\ref{Sec_IndirectQualities}).  Since these qualities cannot
generally be measured directly, they are characterized as indirect qualities.
The relevant indirect qualities are listed in this section, while being
characterized as external, internal, product or process qualities.  The next
subsection lists the relevant direct qualities that assist in achieving the
indirect qualities.  The final subsection presents the methodology that was
employed to summarize, analyze and define each quality.

@@

Many taxonomies have been proposed for software qualities, as in
\citet{McCallEtAl1977, boehm1976quantitative, ISO9126}. Rather than aiming for
complete coverage of the history of qualities, the wide variety of potential
qualities, or the relationships between them, we will instead take a practical
approach; we will focus on the qualities that we have found most relevant in our
research.  This means we will include the usual software engineering suspects,
like usability and maintainability.  In addition, since we also do research on
scientific computing software, we will also include scientifically relevant
qualities, like validatability and reproducibility.

Given our respect for \citet[p.\ 15--33]{GhezziEtAl2003}, we used their list of
qualities as a starting point. Our list, shown in
Table~\ref{Tab_SoftwareQualities}, includes all of their qualities, except for
timeliness, which was excluded because the already included quality of
productivity overlaps with timeliness.  To the list from
\citet{GhezziEtAl2003} we have added the practical quality of installability,
since our aforementioned studies on the state of the practice in different
software domains (for instance \citet{SmithEtAl2018_arXivGIS}) have shown us
that none of the other qualities matter if the software cannot be properly
installed.  Given our interest in scientific computing, we also added the
qualities of validatability and reproducibility. Since we were not able to find
much information in the literature on the quality of verifiability, we also
added the closely related quality of testability.  The quality of sustainability
was added since this term has emerged as a popular goal for software projects.

@@

Table~\ref{Tab_SoftwareQualities} makes a distinction between external and
internal qualities.  External qualities are the qualities that are relevant to
the user of the software while internal qualities are those that are relevant to
developers \citep[p.\ 16]{GhezziEtAl2003}.  Although the users are not typically
interested in internal qualities, it is the internal qualities that influence
external quality.  External qualities are assessed using the produced software
and any user relevant documentation.  Internal qualities reference such things
as the code, documentation, test cases, and the software development process.
Correctness is shown as both an internal and external quality because it is
possible to judge the correctness of software and to judge the correctness of
the various internal artifacts produced while developing the software.  The
external quality of reliability is influenced by the internal quality of
verifiability. Since validatability is related to getting the right
requirements, it is shown as an external quality.  Although one could judge the
usability of internal documentation, the quality of usability is considered as
external, with the quality of understandability designated to cover the internal
equivalent of usability.

Some qualities focus on the product, others on the process, and yet others on
both, as shown in Table~\ref{Tab_SoftwareQualities}.  The term product refers to
both the external and internal products.  The external products are the
user-visible products, like the software itself and any user documentation.  The
internal products are the products (sometimes called work products or artifacts)
relevant to the developers, like requirements documentation, design
documentation, test cases, makefiles, etc.  The process refers to the sequence
of activities that produce the software.  The process generates both the
internal and external products.  The process is based on principles, methods and
techniques.  The process is supported by tools.  All product qualities (internal
and external) are effected by the process, so this information is not shown in
Table~\ref{Tab_SoftwareQualities}.  Instead, the checkmarks in
Table~\ref{Tab_SoftwareQualities} are for qualities that can be applied to a
process.  For instance, we do discuss the installability or correctness of a
process, but it does make sense to think about the portability of a process.
Rather than discuss the performance of a process, we introduce the process
specific quality of productivity.  Similarly, although we can discuss the
usability of a process, we instead introduce the term understandability to
exclusively apply to internal products (like the code).

@@

To achieve the qualities listed in Section~\ref{Sec_IndirectQualities},
conventional wisdom holds that the internal products should aim for the
qualities listed below.  All but the final quality listed (abstraction), are
adapted from the IEEE recommended practice for producing good software
requirements \citep{IEEE1998}. Abstraction is an important software development
principle for dealing with complexity \citep[p .~40]{GhezziEtAl2003}.
\citet{IEEE1998} also includes correctness and verifiability, but we have
excluded these from the list of direct qualities, since they belong in the list
of indirect qualities in the previous section.

@@

\subsection{Methodology}

For each quality we collect as many distinct instances of the definition that we
can find.  Some of the definitions occur in multiple places (for instance the
definitions from \citet{McCallEtAl1977} appear in many software engineering
textbooks).  Since these instances do not add any new information, we do not
make an effort to identify how frequently the definitions reappear in different
sources.  Once all the definitions are collected, we determine the definition
that we would like to work with going forward.  This definition can either be
our preference from the existing definitions, or a new definition, which is
often found by combining existing definitions.

To ensure that our recommended definitions are quality definitions, they are
based on direct quality measures (\ref{SecDirectQsIntro}).  To the list of
direct qualities, we add the quality criteria of measurability.  How the direct
qualities are applied to develop definitions of qualities is described below.

@@

  \item[Completeness] To judge the completeness of our definitions, we verify
  that all of the relevant points from the collected definitions have been
  included.  We also verify that all facets of the definition are covered when a
  quality applies to multiple categories of internal, external, product and/or
  process.  Finally, we check that all of the qualities listed here have been
  considered.

  \item[Consistency] The final list of definitions should be consistent in the
  terminology used.  For instance, we do not use synonyms for variety; we use
  the same word to mean the same concept throughout the final list of
  definitions.  Specific decisions on terminology are as follows:
  \begin{itemize}
    \item To represent the idea of cost, effort, time, resources, and
    efficiency, we say \emph{effort}.
    \item To represent ``the degree to which'' or the ``the extent to which'',
    we will say \emph{the extent to which}.
    \item Fill in as go through definitions.
  \end{itemize}

@@

  \item[Traceability] Each definition includes a section for the rationale.  The
  rationale explicitly links the recommended definition to the previously
  published definitions.  The rationale also explains why any aspects of the
  previous definitions were ignored.  The rationale also traces the selected
  definition to these qualities.

  \item[Unambiguity] With natural language it is difficult to remove all
  ambiguity, but every effort is made to keep the definitions simple and to use
  standard, consistent, terminology.

@@

  \item[Measurability] Although many qualities can only be indirectly measurable,
  the definition of the quality should imply a measure that is conceptually
  possible, even if the data needed to complete the measurement is often
  unavailable.  The scale type of the units of measure are as follows, in order
  of preference: ratio, interval, ordinal and nominal.  These scale types are
  defined in \citet[p.\ 107]{VanVliet2000}.  The ratio and interval scale types
  are preferred to the ordinal and nominal types because more they can convey
  more information.  Specific consequences of aiming for measurability are as follows:
  \begin{itemize}
    \item We will avoid the common phrase in definitions of ``the capability
    of'' because this implies a binary measure.  By this definition a product
    (or process) is either capable or not; it is a binary measure.  Instead of
    measuring capability, we will prefer to use the phrase ``the effort
    required''.
    \item etc.
  \end{itemize}

@@

Our aim is to capture the essence of the quality in an unambiguous way, even if
it cannot be measured. This is analogous to the definition of true error in
scientific computing.  The true error, which is the difference between the
calculated and the true solution, can rarely be calculated since the true
solution is rarely known. Even though it can usually only be estimated, the
concept of true error is still a concept that is relevant for analyzing and
understanding the behaviour of numerical algorithms.

@@

The recommended definition comes from combining Definitions
\ref{Installability_Selected2} and \ref{Installability_Selected1}.  The
different reasons for the proposed definition are as follows:

\begin{itemize}
  \item For consistency uses the term \textbf{effort} in place of efficiency.
  \item For measurability avoids the term ``the capability of'' from
  Definition~\ref{Installability_ISO9126}.
  \item The ``effectiveness'' from Definition~\ref{Installability_Selected2} is
  dropped because installation typically is judged as a binary result.  The
  installation is either completed, or not.
  \item From Definition~\ref{Installability_Selected1} the phrase ``given an
  installation is possible to begin with'' is removed because this notion is
  covered by the measure of effort.  The effort will be infinite if an
  installation is impossible.
\end{itemize}

@@

The selection definition is a rephrasing of
Definition~\ref{Correctness_GhezziEtAl2003}. The different reasons for the
proposed definition are as follows:

\begin{itemize}
  \item Definition~\ref{Correctness_McCallEtAl1977} mentions ``mission
  objectives''.  We feel that the mission objectives are incorporated into the
  specification, so this element is not need to be mentioned separately in the
  recommended definition.
  \item Definition~\ref{Correctness_GhezziEtAl2003} refers to the functional
  specification, but we believe that software is incorrect if it does not
  follow the nonfunctional specification as well.  For instance, for safety
  critical software the performance requirements need to be satisfied, or the
  software will not be trustworthy.
  \item Definition~\ref{Correctness_IEEEComputerDictionary1991} and
  Definition~\ref{Correctness_mcconnell2004code} are almost the same, except
  Definition~\ref{Correctness_IEEEComputerDictionary1991} mentions ``system or
  component'' rather than just ``system''.  To keep our recommended definition
  simple, we do not introduce the distinction of components; we just focus on
  the entities of the software, internal products and processes.
  \item Several of the previous definitions imply measurement of different
  levels of correctness by phrases such as ``The extent to which''
  (Definition~\ref{Correctness_McCallEtAl1977}) and ``The degree to which''
  (Definitions~\ref{Correctness_IEEEComputerDictionary1991}
  and~\ref{Correctness_mcconnell2004code}). However, the proposed definition has
  a binary range of possible measurement - either correct or incorrect.  This
  doesn't follow our stated goal of having the quality of measurement cover the
  largest possible scale type.  We chose to recommend this simpler definition of
  correctness to satisfy the competing quality of unambiguity.
  Definition~\ref{Correctness_IEEEComputerDictionary1991} also implies a binary
  measure with the phrase ``the ability of''.  Making correctness a binary
  quality makes the definition unambiguous and it frees up room for the quality
  of reliability to cover the more nuanced aspects of the extent to which an
  entity is ``correct''.
  \item Internal Product,  Implied by
  Definition~\ref{Correctness_IEEEComputerDictionary1991}.  Changed to mention
  stated and unstated specification (explicit or implicit), since internal
  products do not have a specification.  May have a template.
  \item Process.
\end{itemize}

@@

\begin{mybox}
\subsubsection*{Robustness}
Definition \ref{RobustnessPartialDefn} and Definition
\ref{RobustnessDefnSelected} rephrased: Software possesses the characteristic of
robustness if it behaves ``reasonably'' in two situations: i) when it encounters
circumstances not anticipated in the requirements specification; and ii) when
the assumptions in its requirements specification are violated.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Performance}
Combined definition \ref{PerformanceDefnSelected} and
\ref{PerformanceDefnSelected2}: The degree to which a system or component
accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput (transactions per second),
capacity (concurrent usage loads), and timing (hard real-time demands).
\wss{What is the difference between speed and timing?}
\end{mybox}

@@

This definition offers a comprehensive list of constraints that are commonly
associated with software performance, such as speed, throughput, capacity, and
timing. \pmi{I will check if Wiegers discusses the difference between speed and
timing.} \pmi{Wiegers did not discuss this difference.}  \pmi{Speed - change
over time; timing - related to specification: when something should happen in
relation to something else - state transitions}  \wss{If we need both speed and
timing, we should define them.  We aren't including accuracy from the IEEE
definition.  Is that on purpose?}  \pmi{We have decided not to include accuracy.
SS will find difference b/w speed and timing from a colleague.}   The
different reasons for the proposed definition are as follows:

@@

\begin{mybox}
\subsubsection*{Completeness} 
The first sentence of Definition \ref{CompletenessSelected}: A specification is
complete to the extent that all of its parts are present and each part is fully
developed.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Consistency} 
The first sentence of Definition \ref{ConsistencySelected}: A specification is
consistent to the extent that its provisions do not conflict with each other or
with governing specifications and objectives.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Modifiability} 
The first sentence of Definition \ref{ConsistencySelected}: A specification is
consistent to the extent that its provisions do not conflict with each other or
with governing specifications and objectives.
\end{mybox}

>>>>

\begin{abstract}
	We have found some of the existing definitions of software qualities
	inadequate as a basis for conducting and presenting our software engineering
	research.  Therefore, we have endeavored to create a list of definitions that
	are consistent (same words/phrases are always used for the same concepts),
	measurable (all qualities are conceptually measurable, even if the data needed
	for measurement is often unavailable), abstract (quality definitions state
	what the quality achieves, but not how to achieve it) and traceable (explicit
	links are given to all previous definitions and the ideas within those
	definitions).  Our methodology starts with an exhaustive literature survey to
	find existing definitions.  We then determine the recommended definition,
	which is either one of the existing definitions, or a new definition, found by
	combining existing definitions.  Each recommended definition is accompanied by
	a rationale that explicitly justifies the definition.  By presenting the
	rationales, we hope our software engineering colleagues will scrutinize our
	work and provide recommendations for future modifications. The qualities that
	are defined include installability, correctness, reliability, robustness,
	performance, usability, verifiability, validatability, testability,
	maintainability, reusability, portability, understandability,
	interoperability, productivity, visibility/transparency, reproducibility,
	sustainability, completeness, consistency, modifiability, traceability,
	unambiguity and abstract.  Each quality is classified into one or more of the
	following categories: direct, indirect, internal, external, product or
	process.
\end{abstract}

@@

Quality is defined as a measure of the excellence or worth of an entity.  As is
standard practice, we do not think of quality as a single measure, but rather as
a set of measures.  That is, quality is a collection of different qualities,
often called ``ilities.''  In the overview of managing software quality provided
by \citet[p.~110]{VanVliet2000} the different measures are called quality
attributes, quality factors, and quality criteria.  In \citet{ISO9126} they are
called quality characteristics, sub-characteristics and attributes.  To keep our
presentation simple, and to not imply a classification hierarchy that we don't
intend, we will just use the term qualities to refer to the different measures
of quality.

The qualities of most interest to project managers and users are summarized in
the next subsection (Section~\ref{Sec_IndirectQualities}).  Since these
qualities cannot generally be measured directly, they are characterized as
indirect qualities. The relevant indirect qualities are listed in this section
and each quality is grouped into one or more of the following categories:
external, internal, product or process. The next subsection lists the relevant
direct qualities that assist in achieving the indirect qualities.  The final
subsection presents the methodology that was employed to summarize, analyze and
define each quality.

@@

Many taxonomies have been proposed for software qualities, as in
\citet{McCallEtAl1977, boehm1976quantitative, ISO9126}. Rather than aiming for
complete coverage of the history of qualities, the wide variety of potential
qualities, or the relationships between them, we will instead take a practical
approach; we will focus on the qualities that we have found most relevant in our
research.  This means we will include the usual software engineering suspects,
like usability and maintainability.  Since we also do research on scientific
computing software, we will also include scientifically relevant qualities, like
validatability and reproducibility.

Given our respect for \citet[p.\ 15--33]{GhezziEtAl2003}, we used their list of
qualities as a starting point. Our list, shown in
Table~\ref{Tab_SoftwareQualities}, includes all of their qualities, except for
timeliness, which was excluded because the already included quality of
productivity sufficiently overlaps with timeliness.  To the list from
\citet{GhezziEtAl2003} we have added the practical quality of installability,
since our aforementioned studies on the state of the practice in different
software domains (for instance \citet{SmithEtAl2018_arXivGIS}) have shown us
that none of the other qualities matter if the software cannot be properly
installed.  Given our interest in scientific computing, we also added the
qualities of validatability and reproducibility. Since we found few definitions
in the literature on the quality of verifiability, we also added the closely
related quality of testability.  The quality of sustainability was added since
this term has emerged as a popular goal for software projects.

@@

Table~\ref{Tab_SoftwareQualities} makes a distinction between external and
internal qualities.  External qualities are the qualities that are relevant to
the user of the software while internal qualities are those that are relevant to
developers \citep[p.\ 16]{GhezziEtAl2003}.  Although the users are not typically
interested in internal qualities, it is the internal qualities that influence
external quality.  External qualities are assessed using the produced software
and any user relevant documentation.  Internal qualities reference such things
as the code, documentation, test cases, and the software development process.
Correctness is shown as both an internal and external quality because it is
possible to judge the correctness of software and to judge the correctness of
the various internal artifacts produced while developing the software.  The
external quality of reliability is influenced by the internal quality of
verifiability. Since validatability is related to getting the right
requirements, it is shown as an external quality.  Although one could judge the
usability of internal documentation, the quality of usability is considered as
external, since the quality of understandability designated to cover the internal
equivalent of usability.

Some qualities focus on the product, others on the process, and yet others on
both, as shown in Table~\ref{Tab_SoftwareQualities}.  The term product refers to
both the external and internal products.  The external products are the
user-visible products, like the software itself and any user documentation.  The
internal products are the products (sometimes called work products or artifacts)
relevant to the developers, like requirements documentation, design
documentation, test cases, makefiles, etc.  The process refers to the sequence
of activities that produce the software.  The process generates both the
internal and external products.  The process is based on principles, methods and
techniques while being supported by tools.  All product qualities (internal and
external) are effected by the process, so the checkmarks in
Table~\ref{Tab_SoftwareQualities} are used for a different purpose.  The
checkmarks show which qualities are applied to the process itself.  For
instance, we can consider the correctness and maintainability of a process, but
discussing the portability of a process makes little sense. Rather than apply
the quality of performance to a process, we instead introduce the process
specific quality of productivity.  Although we can imagine discussing the
understandability of a process, to avoid confusion and overlap, we reserve
understandability for the internal quality applied to products (like code). For
the related process quality, we designate the term usability.

@@

To achieve the qualities listed in Section~\ref{Sec_IndirectQualities},
conventional wisdom holds that the internal products should aim for the
qualities listed in this section.  All but the final quality listed
(abstraction), are adapted from the IEEE recommended practice for producing good
software requirements \citep{IEEE1998}. Abstraction is an important addition
because it is the software development principle that allows us to deal with
complexity \citep[p.~40]{GhezziEtAl2003}. \citet{IEEE1998} also includes
correctness and verifiability, but we have excluded these from our list, since
they belong in the list of indirect qualities in the previous section.

@@

\subsection{Methodology} \label{SecMethodology}

For each quality we collect as many distinct instances of the definition that we
can find.  Some of the definitions occur in multiple places (for instance the
definitions from \citet{McCallEtAl1977} appear in many software engineering
textbooks).  Since these instances do not add any new information, they are not
included; we do not make an effort to identify how frequently the definitions
reappear in different sources.  Once all the definitions are collected, we
determine the definition that we would like to recommend.  The recommended
definition can either be our preference from the existing definitions, or a new
definition, which is often found by combining existing definitions.

To ensure that our recommended definitions are quality definitions, they are
based on the direct quality measures (Section~\ref{SecDirectQsIntro}).  To the
list of direct qualities, we also add the quality criteria of measurability.
How the direct qualities are applied to develop quality definitions of qualities
is described below.

@@

  \item[Completeness] To judge the completeness of our definitions, we verify
  that all of the relevant points from the collected definitions have been
  included, or explicitly rejected in the definition's rationale.  We also
  verify that all facets of the definition are covered when a quality applies to
  multiple categories of internal, external, product and/or process.  Finally,
  we check that all of the qualities listed in this section have been
  considered.

  \item[Consistency] The final list of definitions should be consistent in the
  terminology used.  For instance, we do not use synonyms; we use
  the same word or phrase to mean the same concept throughout the final list of
  definitions.  Specific decisions on terminology are as follows:
  \begin{itemize}
    \item To represent the idea of cost, effort, time, resources, and
    efficiency, we say \emph{effort}.
    \item To represent ``the degree to which'' or the ``the extent to which'',
    we will say \emph{the extent to which}.
    \item \wss{Fill in additional consistency decisions, as we go through
    definitions.}
  \end{itemize}

@@

  \item[Traceability] Each definition includes a section for the rationale.  The
  rationale explicitly links the recommended definition to the previously
  published definitions.  The rationale also explains why any aspects of the
  previous definitions were ignored.  The rationale also explicitly traces the
  selected definition to the qualities in this section.

  \item[Unambiguity] With natural language it is difficult to remove all
  ambiguity, but every effort is made to keep the definitions simple and to use
  standard and consistent terminology.  The rationale given for each recommended
  definition also serves the purpose of making the definitions unambiguous.

@@

  \item[Measurability] Although many qualities can only be indirectly measured,
  the definition of the quality should imply a measure that is conceptually
  possible, even if the data needed to complete the measurement is often
  unavailable.  The scale type of the units of measure are as follows, in order
  of preference: ratio, interval, ordinal and nominal.  These scale types are
  defined in \citet[p.\ 107]{VanVliet2000}.  The ratio and interval scale types
  are preferred to the ordinal and nominal types because they can convey more
  information.  Specific consequences of aiming for measurability are as
  follows:
  \begin{itemize}
    \item We will avoid the common phrase in definitions of ``the capability
    of'' because this implies a binary measure.  By this definition a product
    (or process) is either capable or not; it is a binary measure.  Instead of
    measuring capability, we will prefer to use the phrase ``the effort
    required''.
    \item \wss{Add to this list as measurability specific decisions are made.}
  \end{itemize}

@@

Our aim is to capture the essence of the quality in an unambiguous way, even if
it cannot be measured. This is analogous to the definition of true error in
scientific computing.  The true error, which is the difference between the
calculated and the true solution, can rarely be calculated since the true
solution is generally unknown. Even though true error can only be estimated, the
concept of true error is integral to analyzing and understanding the behaviour
of numerical algorithms.

@@

The recommended definition comes from combining
Definitions~\ref{Installability_Selected2} and \ref{Installability_Selected1}.
The rationales for the proposed definition are as follows:

\begin{itemize}
  \item For consistency we use the term \textbf{effort} in place of efficiency.
  \item The ``effectiveness'' from Definition~\ref{Installability_Selected2} is
  dropped because the success or failure of an installation is typically judged
  as a binary result.  The installation is generally either completed, or not.
  \item Although we are okay with a binary result for success or failure of an
  installation, the measure of effort required to complete an installation is
  not a binary measure.  For this reason, we do not use the term ``the
  capability of'' (from Definition~\ref{Installability_ISO9126}), so that we can
  be consistent with our other recommended definitions where we avoid that term
  for measurability reasons.
  \item From Definition~\ref{Installability_Selected1} the phrase ``given an
  installation is possible to begin with'' is removed because this notion is
  covered by the measure of effort.  The effort will be infinite if an
  installation is impossible.
\end{itemize}

@@

The selection definition is a rephrasing of
Definition~\ref{Correctness_GhezziEtAl2003}.  All of the other definitions
(Definition~\ref{Correctness_McCallEtAl1977},
Definition~\ref{Correctness_meyer1988object},
Definition~\ref{Correctness_IEEEComputerDictionary1991} and
Definition~\ref{Correctness_mcconnell2004code}) also mention specification.  The
rationale for the proposed definition follows:

\begin{itemize}
  \item Definition~\ref{Correctness_McCallEtAl1977} mentions ``mission
  objectives''.  We feel that the mission objectives are incorporated into the
  specification, so this element is not need to be mentioned separately in the
  recommended definition.
  \item Definition~\ref{Correctness_GhezziEtAl2003} refers to the functional
  specification, but we believe that correct software also follows the
  nonfunctional specification.  For instance, for safety critical software the
  performance requirements need to be satisfied, or the software will not be
  trustworthy and therefore not correct.
  \item Definition~\ref{Correctness_IEEEComputerDictionary1991} and
  Definition~\ref{Correctness_mcconnell2004code} are almost the same, except
  Definition~\ref{Correctness_IEEEComputerDictionary1991} mentions ``system or
  component'' rather than just ``system''.  To keep our recommended definition
  simple, we do not introduce the distinction of components; we just focus on
  the entities of the software, internal products and processes.
  \item Several of the previous definitions imply measurement of different
  levels of correctness by phrases such as ``The extent to which''
  (Definition~\ref{Correctness_McCallEtAl1977}) and ``The degree to which''
  (Definitions~\ref{Correctness_IEEEComputerDictionary1991}
  and~\ref{Correctness_mcconnell2004code}). However, the proposed definition has
  a binary range of possible measurement -- either correct or incorrect.  This
  doesn't follow our stated goal (in Section~\ref{SecMethodology}) of having the
  quality of measurement cover the largest possible scale type.  Like the
  recommended definition,
  Definition~\ref{Correctness_IEEEComputerDictionary1991} also implies a binary
  measure with the phrase ``the ability of''.  Making correctness a binary
  quality makes the definition unambiguous and it frees up room for the quality
  of reliability to cover the more nuanced aspects of how an entity is
  ``correct''.
  \item Like the recommended definition,
  Definition~\ref{Correctness_IEEEComputerDictionary1991} implies that
  correctness can be judged for products.
  Definition~\ref{Correctness_IEEEComputerDictionary1991} mentions the
  ``specification, design and implementation''.
  \item So that our definition of correctness can be abstract and thus also
  apply to internal products, the definition mentions internal products, and
  states that the specification can be implicit.  To be correct an internal
  product needs to follow any specified template or documentation conventions.
  Moreover, although they may not be stated explicitly, the requirements for a
  document will be implicitly specified in the minds of the products
  authors/creators.
  \item So that our definition of correctness can be abstract and thus also
  apply to processes, the definition mentions processes and states the
  specification can be implicit.  If the rules of the process are explicitly
  specified, then developers can check whether the rules have been followed.
  Even when the rules are not stated in writing, the developers will have
  implicit (possibly changing and inconsistent) rules in their minds.
  \item The definition for correctness allows the specification to be implicit,
  even for the external product of the software itself.  Not every project
  writes down the requirements, but the requirements still exist inside the
  heads of the developers.  This is why testing can be done for software, even
  when the developers do not specify their requirements.
\end{itemize}

@@

\begin{mybox}
\subsubsection*{Robustness}
Definition~\ref{RobustnessPartialDefn} and
Definition~\ref{RobustnessDefnSelected} rephrased: Software possesses the
characteristic of robustness if it behaves ``reasonably'' in two situations: i)
when it encounters circumstances not anticipated in the requirements
specification; and ii) when the assumptions in its requirements specification
are violated.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Performance}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed (database response times, for instance),
throughput (transactions per second), capacity (concurrent usage loads), and
timing (hard real-time demands).
\wss{What is the difference between speed and timing?}
\end{mybox}

@@

The definition is found by combining Definition~\ref{PerformanceDefnSelected}
and Definition~\ref{PerformanceDefnSelected2}.  This definition offers a
comprehensive list of constraints that are commonly associated with software
performance, such as speed, throughput, capacity, and timing. \pmi{I will check
if Wiegers discusses the difference between speed and timing.} \pmi{Wiegers did
not discuss this difference.}  \pmi{Speed - change over time; timing - related
to specification: when something should happen in relation to something else -
state transitions}  \wss{If we need both speed and timing, we should define
them.  We aren't including accuracy from the IEEE definition.  Is that on
purpose?}  \pmi{We have decided not to include accuracy. SS will find difference
b/w speed and timing from a colleague.}   The different reasons for the proposed
definition are as follows:

@@

\begin{mybox}
\subsubsection*{Completeness} 
The first sentence of Definition~\ref{CompletenessSelected}: A specification is
complete to the extent that all of its parts are present and each part is fully
developed.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Consistency} 
The first sentence of Definition~\ref{ConsistencySelected}: A specification is
consistent to the extent that its provisions do not conflict with each other or
with governing specifications and objectives.
\end{mybox}

@@

\begin{mybox}
\subsubsection*{Modifiability} 
The first sentence of Definition~\ref{ConsistencySelected}: A specification is
consistent to the extent that its provisions do not conflict with each other or
with governing specifications and objectives.
\end{mybox}
